\textbf{\sc Towards Deliberative Control of Autonomous Robots}

### 2012-02-09 trunk/related.tex
updates

\begin{figure}[htpb]
 \centering
 \includegraphics[scale=0.3]{figs/planner-arch.pdf}
 \caption{\small A general architectural block diagram for an
   Artificial Intelligence based Planner.}
 \label{fig:planner}
\end{figure}

@@

It was with the demonstration of \texttt{RAX} $65$ Million miles in
outer space, that temporal reasoning using methods came to the
forefront of AI planning and for situated agents. Lessons learned from
\texttt{RAX} led to the development of \texttt{IDEA}
\cite{mus02,mus04} with the central theme of using planners
collectively for problem solving arose. Another critical theme was
iteratively and incremental plan repair of an anytime plan
\cite{Zaimag96} as proposed by \texttt{CASPER}
\cite{chien00}.

@@

Our system, \texttt{T-REX}, the focus of this chapter, is an agent
control structure formally defined as a composition of coordinated
control loops with a recurring sense-plan-act (SPA)
cycle. \texttt{T-REX} was designed after carefully evaluating lessons
learned from \texttt{IDEA} and owes substantially to the notion of
partitioned problem solving from that effort. However this
partitioning is systematic and methodologically principled where we
manage the information flow within the partitioned structure to ensure
consistency in order to direct the flow of goals and observations in a
timely manner. The resulting control structure improves scalability
since many details of each controller can be encapsulated within a
single control loop.  Furthermore, partitioning increases robustness
since controller failure can be localized to enable graceful system
degradation, making this an effective \emph{divide-and-conquer}
approach to the overall control problem.

>>>>

\begin{figure}[htpb]
 \centering
 \includegraphics[scale=0.3]{figs/planner-arch.pdf}
 \caption{\small A general architectural block diagram for an AI based
   Planner.}
 \label{fig:planner}
\end{figure}

@@

It was with the demonstration of \texttt{RAX} $65$ Million miles in
outer space, that temporal reasoning using methods came to the
forefront of AI planning and for situated agents. Lessons learned from
\texttt{RAX} led to the development of \texttt{IDEA}
\cite{mus02,mus04,Dias:2003ua,mus06} with the central theme of using
planners collectively for problem solving arose. Another critical
theme was iteratively and incremental plan repair of an anytime plan
\cite{Zaimag96} as proposed by \texttt{CASPER} \cite{chien00}.

@@

Our system, \texttt{T-REX}, the focus of this chapter, is an agent
control structure formally defined as a composition of coordinated
control loops with a recurring sense-plan-act (SPA) cycle with
deliberation at its core. \texttt{T-REX} was designed after carefully
evaluating lessons learned from \texttt{IDEA} and owes substantially
to the notion of partitioned problem solving from that effort. However
this partitioning is systematic and methodologically principled where
we manage the information flow within the partitioned structure to
ensure consistency in order to direct the flow of goals and
observations in a timely manner. The resulting control structure
improves scalability since many details of each controller can be
encapsulated within a single control loop.  Furthermore, partitioning
increases robustness since controller failure can be localized to
enable graceful system degradation, making this an effective
\emph{divide-and-conquer} approach to the overall control problem.
